An Authoritative Adventure

### 2021-08-12 article.tex
Added a "listparagraph" type that outputs a bolded title with hanging-indent text, used in class features, background options, etc
Expanded the example for the listparagraph format option.

>>>>

\subsubsection{Hanging Indent Features}
The |listparagraph| format allows hanging indented
lists of options, such as those used for class features,
background skill/tool proficiency options, and
sometimes area features, for example:

\listparagraph[6pt]{Doors}
{The doors are made from thick lumber and are unlocked.}

\listparagraph{Light}
{The area is illuminated by candles placed in sconces on the
walls. Each candle has had a \textit{continual flame} spell
cast on it. Dispelling a flame is rumoured to give grievous offence
to the host.}

\listparagraph{Ventilation}
{All areas contain an adequate air supply. The air is renewed
via lung-like sacks that cling to the ceiling.}
